Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-07-23 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
adding updated figures to text, changes in description, added some more concluding marks in Results

\documentclass[preprint2,linenumbers]{aastex}

@@

	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$), with significant consequences. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEU, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

	\par\authorcomment1{More discussion here? Some conclusions? What else do we need to say? Lead in to the next point a bit better? Maybe some discussion of why the slopes are different? What slopes we should expect? Refer to Paper 1...}

@@

@@

		\caption{Histograms of emission measure ratios for all heating function types and heating frequencies for the case in which only the electrons are heated. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}. \textbf{Left:} Emission measure ratios separated by heating function type. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, only five values of $t_N$ are shown.}

@@

		\caption{Same as \autoref{fig:em_ratio_hist_el}, but for the case where only the ions are heated.}

@@

	\par Such an emission measure ratio also provides a way to compare in a concise way every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value. The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e. $\beta=0$). We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same. Here we have not included the uniform heating case due to small number statistics (i.e. $<20$ emssion measure ratios). 

@@

	\par The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes. We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$. For $t_N>4000$ s, the emission measure ratio seems to be more sensitive to the heating frequency .

@@

	\par Similarly, we compute the same emission measure ratio for the case in which only the ions are heated. The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function. Similar to the electron heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measure ratios is relatively insensitive to $\alpha$. However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim0.5$ for $\beta=0$ and $>1$ for $\beta=1$. Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$. The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$. With the exception of the $t_N=2000$ s and $t_N=3000$ s group, the distributions for each value of $t_N$ are much more spread out (as compared \autoref{fig:em_ratio_hist_el}). In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5. In general, the emission measure ratios in the ion heating case appear to be more sensitive to $t_N$ compared to the electron heating case.

@@

	\software{IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, Scipy \citep{van_der_walt_numpy_2011}}

>>>>

\documentclass[preprint,linenumbers]{aastex}

@@

	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$), with significant consequences. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEI, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

	\par Our results here suggest that while $a$ is an adequate parameter for describing the cool side of $\mathrm{EM}(T)$, the functional form $\mathrm{EM}\sim T^{-b}$ does not adequately capture the character of the hot part of $\mathrm{EM}(T)$ over any reasonable temperature range. \citep{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included. However, in \citetalias{barnes_inference_2016}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold. In this way, we should not expect to recover these analytic values from our numerical or observational results. Clearly, we need an alternate metric to assess the amount of hot plasma seen by the emission measure distribution.
	\par\authorcomment1{I think discussing the results of this section in the context of Paper 1 is a good idea. Not sure how well this works...needs something else?}

@@

		\plottwo{figures/ratio_hist_alpha_single_T2.pdf}{figures/ratio_hist_twait_single_T2.pdf}
		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}$ K, for all heating function types and heating frequencies for the single fluid case. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citep{scargle_studies_2013} as implemented in the astroML Python package for statistical learning in astronomy \citep{vanderplas_introduction_2012}. \textbf{Left:} Emission measure ratios separated by heating function type for all heating frequencies, $250\le t_N\le5000$ s. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, only five values of $t_N$ are shown, $t_N=1000,2000,3000,4000,5000$ s.}
		\label{fig:em_ratio_hist_single}

@@

		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the electrons are heated.}

@@

		\caption{Same as \autoref{fig:em_ratio_hist_single}, but for the case where only the ions are heated. Here, the bin widths are calculated according to the well-known Freedman-Diaconis formula \citep{freedman_histogram_1981}}

@@

	\par Such an emission measure ratio also provides a way to compare in a concise way every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value. The left panel of \autoref{fig:em_ratio_hist_single} shows the single-fluid case, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e. $\beta=0$). We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same. Here we have not included the uniform heating case due to small number statistics (i.e. $<20$ emssion measure ratios). 

@@

	\par The right panel of \autoref{fig:em_ratio_hist_single} shows these same emission measure ratios, but now separated by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes. For $t_N\le3000$ s, the results cluster just below 0.5 while the $t_N=4000,5000$ s cases peak at $\sim0.6$ and $\sim0.9$, respectively. In general, it seems that the distribution widens as $t_N$ increases.

@@

	\par Similarly, \autoref{fig:em_ratio_hist_el} shows the emission measure ratio for the case in which only the electrons are heated. Looking first at the left panel, we see that, as in \autoref{fig:em_ratio_hist_single}, the emission measure ratio is largely insensitive to $\alpha$, but is comparatively more narrow and falls off more quickly twoard higher emission measure ratios. The $\beta=0$ cases (for all $\alpha$) peak near $0.25$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1. Again, we have not included the uniform case. The right panel shows the same emission measure ratios now grouped by $t_N$. The lower frequencies, $t_N=1000,2000,3000$ s, tend to cluster at approximately the same value as in \autoref{fig:em_ratio_hist_el}. However, for all $t_N$, the distributions are significantly more narrow. Furthermore, the lower heating frequencies, $t_N=4000,5000$ s, peak at considerably lower lower values, $\sim0.45$ and $\sim0.7$, respectively. Overall, for all $t_N$ in the electron heating case, the emission measure ratio distributions tend to be comparatively narrow and clustered near $0.5$.
	\par Finally, we compute the same emission measure ratio for the case in which only the ions are heated. The left panel of \autoref{fig:em_ratio_hist_ion} shows histograms for each type of heating function. Similar to the electron heating results, we find that the $\beta=0$ distributions peak at lower values compared to the $\beta=1$ distributions and that in the $\beta=0$ case, the distribution of emission measure ratios is relatively insensitive to $\alpha$. However, unlike the electron heating case, the distributions in all cases are much wider and peak at higher values, $\sim0.5$ for $\beta=0$ and $>1$ for $\beta=1$. Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$. The right panel of \autoref{fig:em_ratio_hist_ion} shows the same emission measure ratios now grouped by waiting time where again we only show five values of $t_N$. With the exception of the $t_N=2000$ s and $t_N=3000$ s group, the distributions for each value of $t_N$ are much more spread out (as compared to \autoref{fig:em_ratio_hist_single} and \autoref{fig:em_ratio_hist_el}). In particular, $t_N=5000$ s peaks above 1.0 and extends past 1.5 while $t_N=1000$ peaks near 0 and drops off very steeply before 0.5. In general, the emission measure ratios in the ion heating case appear to be more sensitive to $t_N$ compared to the electron heating case.

@@

	\software{astroML \citep{vanderplas_introduction_2012}, IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, Scipy \citep{van_der_walt_numpy_2011}}
